Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
meta-estimators

Some machine learning algorithms are most naturally expressed
as modification or extensions of other, simpler algorithms.
Examples include ensemble estimators
and various multiclass and multilabel classification schemes.
Such algorithms are implemented as so-called ``meta-estimators'',
that take an estimator as input and use that to perform learning and prediction.

As an example, a logistic regression classifier
by default uses a one-vs.-rest (aka one-vs.-all) scheme internally
for performing multiclass classification.
If multiclass classification based on error-correcting codes
\citep{dietterich1995solving} is desired instead,
this can achieved with an \texttt{OutputCodeClassifier}
that wraps a \texttt{LogisticRegression}:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression
from sklearn.multiclass import OutputCodeClassifier

>>>>

In machine learning, some algorithms are expressed as meta-algorithms built
and parametrized on simpler algorithms. Examples include ensemble methods which
build and combine several simpler models (e.g., decision trees), or multiclass
and multilabel classification schemes which can be used to turn a binary
classifier into a multiclass or multilabel classifier. In \sklearn, such algorithms are
implemented as \textit{meta-estimators}. They take as input an existing base
estimator and use it internally for learning and making predictions.

As an example, a logistic regression classifier
 uses by default a one-vs.-rest  scheme
for performing multiclass classification.
If multiclass classification based on error-correcting codes
\citep{dietterich1995solving} is desired instead,
then this can achieved  using an \texttt{OutputCodeClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression
from sklearn.multiclass import OutputCodeClassifier
